The Types and Driving Forces of Modifications in the Evolution of an API

### 2015-05-11 thesis/paper.tex
Tables in BG+Title

\title{Exploring the Types and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}

@@

>>>>

\title{The Types and Driving Forces of Modifications in the Evolution of an API}

@@

              \textbf{Type}                              & \textbf{Explanation}    \\ \midrule
              Corrective    & [Explanation]                      \\ \hline
              Reductive     & [Explanation]                     \\ \hline
              Adaptive      & [Explanation]                      \\ \hline
              Performance   & [Explanation]                     \\ \hline
              Preventive    & [Explanation]                      \\ \hline
              Groomative    & [Explanation]                      \\ \hline
              Updative      & [Explanation]                     \\ \hline
              Reformative   & [Explanation]                     \\ \hline
              Evaluative    & [Explanation]                     \\ \hline
              Consultive    & [Explanation]                     \\ \hline
              Training      & [Explanation]                     \\

       \end{tabular}
       \caption{Explanation of Types of Software Maintenance}
       \label{table:expl_types}
\end{table}

Adaptive

              \textbf{Law}                              & \textbf{Explanation}    \\ \midrule
              Continuing Change                         & [Explanation]                      \\ \hline
              Increasing Complexity                     & [Explanation]                     \\ \hline
              Self Regulation                           & [Explanation]                      \\ \hline
              Conservation of Organisational Stability  & [Explanation]                     \\ \hline
              Conservation of Familiarity               & [Explanation]                      \\ \hline
              Continuing Growth                         & [Explanation]                      \\ \hline
              Declining Quality                         & [Explanation]                     \\ \hline
              Feedback System                           & [Explanation]                      \\

       \end{tabular}
       \caption{Explanation of Lehman's Laws}
       \label{table:expl_laws}
\end{table}
